### 2017-03-28 drafts/task_referral/introduction.tex
removed reaveal.js stuff

On--demand workers have expressed frustration with the algorithmic management that largely dictates their work
\cite{uberAlgorithm}.
The fear of deviating from expected results causes online information workers 
--- such as workers on Amazon Mechanical Turk (AMT), or ``Turkers'' ---
to avoid creative or open--ended tasks due to the perceived riskiness of
investing a significant amount of time into a task only to be rejected.
\ali{[citation needed]}
\citeauthor{haas2015argonaut} address some of these problems by bootstrapping
human reviewers from vetted crowd workers
\cite{haas2015argonaut}.

>>>>

On--demand workers have expressed frustration with the algorithmic management that largely dictates their work
\cite{uberAlgorithm}. \msb{blah blah blah}
The fear of deviating from expected results causes online information workers 
--- such as workers on Amazon Mechanical Turk (AMT), or ``Turkers'' ---
to avoid creative or open--ended tasks due to the perceived riskiness of
investing a significant amount of time into a task only to be rejected.
\ali{[citation needed]}
\citeauthor{haas2015argonaut} address some of these problems by bootstrapping
human reviewers from vetted crowd workers
\cite{haas2015argonaut}.
